Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-03-12 eswc-2012/phdsymp.tex
typo
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@179 43ef1190-90fd-4dd7-a769-d0121f02b80e

Finally, I have seen little work on the problem of rapidly changing
data, so the adaption of existing techniques to such situations may
also be a interesting.

>>>>

Finally, I have seen little work on the problem of rapidly changing
data, so the adaption of existing techniques to such situations may
also be interesting.
